Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-13 paper.tex

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/cophylogeny_wide.pdf}
\caption{\label{fig:cophylogeny} DESCRIBE ME. See
Figure~\ref{fig:cophlogeny_long} for the equivalent cophylogeny
for the Long ARG.
}
\end{figure}

@@

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/supp_cophylogeny_long.pdf}
\caption{\label{fig:cophlogeny_long}Copyhlogeny for the Long ARG. MORE DETAIL.}
\end{figure}

>>>>

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/cophylogeny_wide.pdf}
\caption{\label{fig:cophylogeny} Tanglegram comparing the first local tree in the
wide ARG (sampled to mid-2021) and an “all-time” global NextStrain tree (sampled
to January 21, 2023). The trees were pruned down to the samples present in both
the trees. Light grey lines match the corresponding samples between the two
trees; black circles indicate identical sample partitions between the two trees.
Terminal branches are colour-coded according to the Pango lineage status
assigned to the tip samples; no Pango recombinants are shown, as none are shared
between the trees. The tanglegram was generated with the aid of the Neighbor-Net
algorithm \citep{Scornavacca2011-mg} implemented in Dendroscope
version 3.8.5 \citep{Huson2012-ys}. See Figure~\ref{fig:cophlogeny_long} for the equivalent cophylogeny
for the Long ARG.}
\end{figure}

@@

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/supp_cophylogeny_long.pdf}
\caption{\label{fig:cophlogeny_long}Tanglegram equivalent to that in
Figure~{fig:cophlogeny}, but for the long ARG (i.e. subsampled to mid-2022). }
\end{figure}
